---
title: '**`renv` part 2: `dplyr 0.8.0`** '
author: "Marisa and Fei"
date: "`r Sys.Date()`"
output:
  html_document: 
    code_folding: show
    theme: cosmo
---
<!-- make font a bit bigger for presentation purposes --> 

<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 16px;
}
code.r{ /* Code block */
    font-size: 16px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 16px;
}
</style>


```{r setup, message = FALSE, warning = FALSE, echo = FALSE}
# global knitr options
library(knitr)
opts_chunk$set(fig.align = "center", echo = TRUE, warning = TRUE, message = TRUE)
```

```{r, warning = FALSE, message = FALSE}
library(renv)
# give consent for renv to run in Rmd
renv::consent(provided = TRUE) 

# load libraries from previous renv::snapshot
# renv::revert(commit = "2d9c6914c1995721bf1b8149afa6997d25010d00")
renv::restore()
```

```{r, warning = FALSE, message = FALSE}
library(assertthat)
library(kableExtra)
library(maptools)
library(sf)
library(sp)
library(spdep)
library(raster)
library(leaflet)
library(tmap)
library(tmaptools)
library(RColorBrewer)
library(tidyverse)
library(dplyr)
```

Note that I now have **`dplyr` version 0.8.0**. loaded:
```{r}
packageVersion("dplyr")
```


```{r, echo = FALSE}
# load data
dat <- read.csv("data/ghi_hrrp.csv")
dat <- dat %>% filter(!is.na(excess_readmission_ratio))

state_sf <- sf::st_read("data/cb_2016_us_state_20m/cb_2016_us_state_20m.shp") 
county_sf <- sf::st_read("data/cb_2016_us_county_20m/cb_2016_us_county_20m.shp") 

# add geoid as unique identifiers for states and counties -----------------

# state dictionary
st_dict <- state_sf %>% st_drop_geometry() %>% 
  dplyr::select(geoid_st = STATEFP, state = STUSPS)

dat_cnty_lst <- dat %>% dplyr::select(county_name, state) %>% distinct() %>%
  mutate(key = str_c(state, tolower(county_name), sep = "_"))

# side note Q: some counties could have more than one GEOIDs, why?
# for demo purpose: just pick one
# cnty_dict_sf <- county_sf %>% st_drop_geometry() %>% select(STATEFP, GEOID, county_name = NAME) %>%
#   group_by(STATEFP, county_name) %>%
#   mutate(n = n()) %>%
#   arrange(desc(n))

cnty_dict_sf <- county_sf %>% st_drop_geometry() %>% 
  dplyr::select(STATEFP, GEOID, county_name = NAME) %>% 
  left_join(state_sf %>% st_drop_geometry() %>% 
              dplyr::select(STATEFP, state = STUSPS), 
            by = "STATEFP") %>%
  mutate(key = str_c(state, tolower(county_name), sep = "_"))

dat_cnty_lst <- dat_cnty_lst %>%
  left_join(cnty_dict_sf, by = "key", suffix = c("_hrrp", "_cnty_sf")) %>%
  group_by(key) %>%
  mutate(cnt = n(),
         num = row_number()) %>%
  filter(
    !is.na(STATEFP),
    row_number() == 1  # only select the first record if there is multiple geoids per county
    ) %>%
  ungroup()

cnty_dict <- dat_cnty_lst %>%
  dplyr::select(county_name = county_name_hrrp, 
                state = state_hrrp, geoid_cnty = GEOID)

dat_w_key <- dat %>%
  left_join(st_dict, by = "state") %>%
  left_join(cnty_dict, by = c("state", "county_name"))
```

```{r}
# err_sum 
err_sum <- function(df, group_var) {  # err = excess readmission ratio : )
  df %>%
    group_by_(group_var) %>% 
    summarise(mean = mean(excess_readmission_ratio), 
              median = median(excess_readmission_ratio), 
              sd = sd(excess_readmission_ratio), 
              n = n())
}
```

Now let's say we wanted to summarize the excess readmission ratio for just one measure, e.g. AMI.

There are a number of ways we could accomplish this: 
 - pass a filtered dataframe to the `err_sum` function e.g. ` err_sum(dat %>% filter(measure_name == "AMI", "hospital_ownership")`
 - use the `nest` function e.g. `dat_nested <- dat %>% group_by(measure_name) %>% nest()` and then `map(dat_nested[["data"]], ~err_sum(.x, "hospital_ownership"))`, 
 - Write another function that filters our data and then calls `err_sum`
 
```{r}
tab3 <- dat %>%
  filter(measure_name == "AMI") %>% 
  group_by(hospital_ownership) %>% 
  summarise(mean = mean(excess_readmission_ratio), 
            median = median(excess_readmission_ratio), 
            sd = sd(excess_readmission_ratio), 
            n = n())

tab3 %>%
  kable %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r}
err_sum_filtered <- function(group_var, filter_var, filter_value) {  
 dat_filtered <- dat %>%
    filter_(paste0(filter_var, " == ", "'", filter_value,"'"))
 
  err_sum(dat_filtered, group_var)
}

tab4 <- err_sum_filtered(group_var = "hospital_ownership", 
                         filter_var = "measure_name",  
                         filter_value = "AMI")
```

Check new function is working as expected: 

```{r}
are_equal(tab3, tab4)
```

Now we can get summary statistics across various grouping variables for each measure.

```{r}
measures <- levels(dat$measure_name)
results <- map(measures, 
               ~err_sum_filtered(group_var = "hospital_ownership", 
                                 filter_var = "measure_name", 
                                 filter_value = .x))
names(results) <- measures
```

# {.tabset .tabset-fade .tabset-pills}

```{r}
fct_summarise_hrrp <- function(dat, report_lvl, measr){
  
  # input:
  #   dat - a data frame, with records of readmission rate per hospital per measure
  #   report_lvl - a string, either "state" or "county"
  #   measr - a string, measure name. 
  # output:
  #   corr_mtrx - correlation matrix between measures
  #   map - a list of tmap objects: continental, Hawaii, and Alaska
  
  index <- list(
    state = list(shape_file = state_sf, key = "geoid_st"),
    county = list(shape_file = county_sf, key = "geoid_cnty")
  )
  
  var_key <- sym(index[[report_lvl]][["key"]])
  
  dat_clean <- dat %>%
    dplyr::select(hospital_name, provider_id, !!var_key, measure_name,
           excess_readmission_ratio, 
           predicted_readmission_rate, 
           expected_readmission_rate) %>%
    filter(!is.na(excess_readmission_ratio) & !is.na(!!var_key)) %>%
    group_by(!!var_key, measure_name) %>%
    summarise(err = sum(predicted_readmission_rate)/sum(expected_readmission_rate)) %>%
    spread(key = measure_name, value = err) %>%
    ungroup
  
  corr_mtrx <- dat_clean %>% 
    dplyr::select(-!!var_key) %>%
    cor(method = "pearson", use = "pairwise.complete.obs")
  
  hrrp_sf <- index[[report_lvl]][["shape_file"]] %>%
    left_join(dat_clean, by = c("GEOID" = index[[report_lvl]][["key"]]))
  
  # HI - 15, AK - 02
  us_continental_map <- tm_shape(hrrp_sf %>% 
                                   filter(!str_sub(GEOID, 1, 2) %in% c("15", "02")), 
                                 projection = 2163) +
    tm_fill(col = measr, palette = "OrRd", n = 4) +
    tm_borders(col = "grey50") +
    tm_layout(frame = FALSE, 
              legend.position = c("right","bottom"),
              main.title = str_c("Risk-adjusted readmission rate of ", measr, 
                                 " by ", report_lvl))
  
  hawaii_map <- tm_shape(hrrp_sf %>% filter(str_sub(GEOID, 1, 2) == "15")) +
    tm_fill(col = measr, palette = "OrRd", n = 4, legend.show = F) +
    tm_borders(col = "grey50")+
    tm_layout(title = "Hawaii", frame = FALSE, bg.color = NA, 
              title.position = c("left", "bottom"))
  
  alaska_map <- tm_shape(hrrp_sf %>% filter(str_sub(GEOID, 1, 2) == "02"), 
                         projection = 2163) +
    tm_fill(col = measr, palette = "OrRd", n = 4, legend.show = F) +
    tm_borders(col = "grey50")+
    tm_layout(title = "Alaska", frame = FALSE, bg.color = NA)
  
  return(list(
    corr_mtrx = corr_mtrx,
    map = list(
      continental = us_continental_map,
      hawaii = hawaii_map,
      alaska = alaska_map)
  ))
}
```


## **AMI**
```{r}
results$AMI %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r state_map_ami}
output <- fct_summarise_hrrp(dat_w_key, "state", "AMI")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_ami}
output <- fct_summarise_hrrp(dat_w_key, "county", "AMI")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


## **CABG**
```{r}
results$CABG %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r state_map_cabg}
output <- fct_summarise_hrrp(dat_w_key, "state", "CABG")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_cabg}
output <- fct_summarise_hrrp(dat_w_key, "county", "CABG")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```

## **COPD**
```{r}
results$COPD %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r state_map_copd}
output <- fct_summarise_hrrp(dat_w_key, "state", "COPD")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_copd}
output <- fct_summarise_hrrp(dat_w_key, "county", "COPD")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```
 
## **HF**
```{r}
results$HF %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r state_map_hf}
output <- fct_summarise_hrrp(dat_w_key, "state", "HF")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_hf}
output <- fct_summarise_hrrp(dat_w_key, "county", "HF")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```

## **HIP_KNEE**
```{r}
results$HIP_KNEE %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r state_map_hipknee}
output <- fct_summarise_hrrp(dat_w_key, "state", "HIP_KNEE")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_hipknee}
output <- fct_summarise_hrrp(dat_w_key, "county", "HIP_KNEE")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```

## **PN**
```{r}
results$PN %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

# 

```{r state_map_pn}
output <- fct_summarise_hrrp(dat_w_key, "state", "PN")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```


```{r county_map_pn}
output <- fct_summarise_hrrp(dat_w_key, "county", "PN")

output$map$continental
print(output$map$alaska, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
print(output$map$hawaii, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
```

```{r}
dat %>% 
  group_by(hospital_ownership) %>% 
  group_walk(~write.csv(.x, file = paste0("output/", .y$hospital_ownership, ".csv")))
```

Underscore methods from `dplyr` are being deprecated, so we should use the standard `dplyr` functions (i.e. not the underscore versions) and use non-standard evaluation (NSE). Read up on tidyeval [here](https://tidyeval.tidyverse.org) and watch a 5 min video overview of NSE from Hadley [here](https://www.youtube.com/watch?v=nERXS3ssntw).

```{r}
err_sum <- function(df, group_var) {  
  
  group_var <- enquo(group_var)
  
  df %>%
    group_by(!!group_var) %>% 
    summarise(mean = mean(excess_readmission_ratio), 
              median = median(excess_readmission_ratio), 
              sd = sd(excess_readmission_ratio), 
              n = n())
}

err_sum_filtered <- function(group_var, filter_var, filter_value) {  
  group_var <- enquo(group_var)
  filter_var <- enquo(filter_var)

    dat_filtered <- dat %>%
    filter((!!filter_var) == filter_value)
 
  err_sum(dat_filtered, !!group_var) 
}
```

```{r}
results2 <- map(measures, 
               ~err_sum_filtered(group_var = hospital_ownership, 
                                  filter_var = measure_name, 
                                  filter_value = .x))
names(results2) <- measures
```

Check for equivalence: 
```{r}
assert_that(sum(map2(results, results2, ~!all_equal(.x, .y)) %>% unlist()) == 0)
```


