---
title: '**`renv` part 3: back to `dplyr 0.7.6`** '
author: "Marisa and Fei"
date: "`r Sys.Date()`"
output:
  html_document: 
    code_folding: show
    theme: cosmo
---
<!-- make font a bit bigger for presentation purposes --> 

<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 16px;
}
code.r{ /* Code block */
    font-size: 16px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 16px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = FALSE, message = FALSE}
library(renv)
# give consent for renv to run in Rmd
renv::consent(provided = TRUE) 

# load libraries from previous renv::snapshot
# renv::revert(commit = "2c4179af7f118f34c93dca61d88a606c2946540b")
renv::restore()
```
 
```{r, warning = FALSE, message = FALSE}
library(assertthat)
library(kableExtra)
library(maptools)
library(sf)
library(sp)
library(spdep)
library(raster)
library(leaflet)
library(tmap)
library(tmaptools)
library(RColorBrewer)
library(tidyverse)
library(dplyr)
```

Check the version of `dplyr` loaded:
```{r}
packageVersion("dplyr")
```


```{r, error = TRUE}
dat <- read.csv("data/ghi_hrrp.csv")
dat <- dat %>% filter(!is.na(excess_readmission_ratio))

dat %>% 
  group_by(hospital_ownership) %>% 
  group_walk(~write.csv(.x, file = paste0("output/", .y$hospital_ownership, ".csv")))
```

# `renv` pros/cons

Pros 
- Reproducibility!
- Easy to add to R projects
- Easy (in theory -- haven't actually tried this yet) to migrate a `packrat` project to `renv`
- Integration with git and ability to look back at packages/dependencies in different git commits
- Can be used with Docker
- Still being actively developed, so not as integrated with Rstudio as `packrat` (yet)

Cons
- `renv` snapshots are only stored in history after a git commit
- Still being actively developed, so not as integrated with Rstudio as `packrat` (yet)

